### 2020-11-10 presentation/1_setting.tex
Delete obsolete formulation on SOCP

\I Problem (a): How to recover the channel with fewer measurements?

\I Problem (b): How to design precoders and combiners?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Channel Model and Beamformers}
{
\I Given channel \m {\M {H} \in \NC \MB {C} ^{N_H \D N_H}} with uniform linear array

\I Complex standard normal noise \m {\m {Z} \in \NC \MB {C} ^{N_H \D N_H}}

\I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_R \D N_Y}}
\I Tx: Analog precoder \m {\NC \M {F}_R \in \NC \MB {C} ^{N_H \D N_R}}

\I Rx: Digital combiner \m {\M {W}_B \in \NC \MB {C} ^{N_R \D N_H}}
\I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_Y \D N_R}}

\I Magnitude constraint \m {\Nm {\M {F}_R \SB {n_H, n_R}} = 1}, \m {\Nm {\M {W}_R \SB {n_R, n_H}} = 1} 
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Problem Description}
{
\I We have \m {\M {Y} =\M {W}_B \M {W}_R \RB {\M {H} \M {F}_R \M {F}_B +\M {Z}}}
%
\I Problem (a): How to recover \m {\M {H}} with knowledge of \m {\M {Y}}?

@@

\I What kind of matrices faciliates our goal?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Cast to Linear System}
{
\I Introduce the DFT matrix \m {\M {K} \in \NC \MB {C} ^{N_H \D N_H}}, and write
\Disp {
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}},
\Q \M {P}
:= \RB {\M {F}_B^\Tr \M {F}_R^\Tr \m {K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}, \NR
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {K}^\Adj \M {H} \M {K}},
\Q \V {z}
:= \Rm {vec} \SB {\M {Z}} \NR
}

@@

\I Can we find a basis on which \m {\V {g}} is sparse?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Literature on Compressive Sensing}
{
\I Bajwa, Haupt, Sayeed, and Nowak (2010): MIMO, linear invariant system, using Dantzig Selector (DS)

\I Alkhateeb, Ayach, Leus, Heath (2014): mm-wave, adaptive training algorithm for given codebook

@@

\I Lee, Lee, and Yong (2016): MIMO mm-wave, hybrid beamforming, using Orthogonal Matching Pursuit (OMP)
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Questions}
{
\I How does greedy algorithms (like OMP) trade precision for complexity, and that the opposite is true of convex programs (like DS)?

@@

\I We give a bound (holding for high probability) on expected error norm

\I Numerical results illustrate that in our configuration DS is superior to OMP among other methods, but is achieved at the cost of higher complexity.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Design of Beamformers}
{
\I We set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ complex standard normal, up to a design constant

@@

\I We argue that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, thus \m {\M {P}} has too.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Applying Dantzig Selector}
{
\I Fix sparsity \m {s = L \RB {\log N_H}^2} for definiteness.

\I Input \m {\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}}, \m {\g_{\Ss {DS}} \geq 0}.

>>>>

\I Problem (a): How to reconstruct the channel with fewer measurements?

\I Problem (b): How to design precoders and combiners?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Channel Model and Beamformers}
{
\I Given MIMO channel representation \m {\M {H} \in \NC \MB {C} ^{N_H \D N_H}} with uniform linear array, having \m {L} paths.

\I Complex standard normal noise \m {\M {Z} \in \NC \MB {C} ^{N_H \D N_H}}

\I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_R \D N_B}}
\I Tx: Analog precoder \m {\NC \M {F}_R \in \NC \MB {C} ^{N_H \D N_R}}

\I Rx: Digital combiner \m {\M {W}_B \in \NC \MB {C} ^{N_R \D N_H}}
\I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_B \D N_R}}

\I Magnitude constraint \m {{\Nm {\M {F}_R}_{\SB {n_H, n_R}}} = 1}, \m {{\Nm {\M {W}_R}_{\SB {n_R, n_H}}} = 1} 
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Problem Description}
{
\I We have \m {\M {Y} =\M {W}_B \M {W}_R \RB {\M {H} \M {F}_R \M {F}_B +\M {Z}}}
%
\I Problem (a): How to recover \m {\M {H}} with knowledge of \m {\M {Y}}?

@@

\I What kind of matrices facilitates our goal?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Cast to Linear System}
{
\I Introduce the DFT matrix \m {\M {K} \in \NC \MB {C} ^{N_H \D N_H}}, and write
\Disp {
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}},
\Q \M {P}
:= \RB {\M {F}_B^\Tr \M {F}_R^\Tr \m {K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}, \NR
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {K}^\Adj \M {H} \M {K}},
\Q \V {z}
:= \Rm {vec} \SB {\M {Z}} \NR
}

@@

\I Can we find a basis on which \m {\V {g}} is likely to be sparse?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Literature on Compressive Sensing}
{
\I Bajwa, Haupt, Sayeed, and Nowak (2010): MIMO, linear invariant system, using Dantzig Selector (DS)

\I Alkhateeb, Ayach, Leus, Heath (2014): mm-wave, adaptive training algorithm for given sensing matrix

@@

\I Lee, Lee, and Yong (2016): MIMO mm-wave, hybrid beamforming, using Orthogonal Matching Pursuit (OMP)
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Questions}
{
\I Does greedy algorithms (like OMP) trade precision for complexity, and is the opposite true of convex programs (like DS)?

@@

\I We give a bound (holding for high probability) on expected error norm.

\I Numerical results illustrate that in our configuration DS is superior to OMP among other methods, at the cost of higher complexity.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Design of Beamformers}
{
\I We set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ complex standard normal, up to a design constant

@@

\I We argue that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have restricted isometry, thus \m {\M {P}} has too.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Applying Dantzig Selector}
{
\I Fix sparsity \m {s = L \RB {\log N_H}^2} for definiteness.

\I Input \m {\M {P} \in \MB {C} ^{N_B^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}}, \m {\g_{\Ss {DS}} \geq 0}.

### 2020-11-10 presentation/2_analysis.tex
Delete obsolete formulation on SOCP

\Frame {Error Analysis}
{
\I What's the difference of true value \m {\V {h}} and estimated value \m {\Hat {\V {h}}}?

\I Should consider that \m {\V {g}} is not strictly sparse

\I Should justify that if beamformers, \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, have RIP for high probability, than \m {\m {P}} does too.

\I Should bound the big \m {\MC {O}} of error norm corresponding to these failure events.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {The Bound}
{
\I We argue in the treatise that it holds for probability \m {p} that
\Disp {
\NC \VNm {\Hat {\V {g}} - \V {g}} _2
%
\leq \NC 8 \R {L} \RB {\log N_H} ^{3/2} \NR
}
%
\I For ideal values
\Disp {
\NC N_Y \gtrsim \NC 4 \log N_H, \Q
N_R \gtrsim 16 L \RB {\log N_H}^2 \NR
}
%
\I And it holds that
\Disp {
\NC 1 - p
\lesssim \NC 2 N_H ^{-1/3} \NR
}
%
\I Unfortunately, the values are too big to simulate.
}

>>>>

\Frame {Error Analysis}
{
\I Can we bound \m {\VNm {\V {h} -\Hat {\V {h}}} _2}?

\I Does it matter that \m {\V {g}} is not strictly sparse?

\I If \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, all have restricted isometry, does \m {\m {P}} have too?

\I Big \m {\MC {O}} probability of failure events?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {The Bound}
{
\I We argue in the treatise that it holds for probability \m {p} that
\Disp {
\NC \VNm {\Hat {\V {g}} - \V {g}} _2
%
\eqsim \NC \MC {O} \SB {\R {L} \RB {\log N_H} ^{3/2}} \NR
}
%
\I For ideal values
\Disp {
\NC N_B \gtrsim \NC 4 \log N_H, \Q
N_R \gtrsim 16 L \RB {\log N_H}^2 \NR
}
%
\I And it holds that
\Disp {
\NC 1 - p
\eqsim \NC \MC {O} \SB {\Ss {e} ^{-N_B /12}}
 \NR
}
%
\I Unfortunately, the values are too big to simulate.
}

### 2020-11-10 presentation/3_simulation.tex
Delete obsolete formulation on SOCP

% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Linear Programming}
{
\I DS is equivalent to a linear program, which allows more efficient convex programming methods to be used.

\I Calculate
\Disp {
\NC \Hat {\V {g}}, \Hat {\V {f}}
\LA \NC \startcases
   \NC \Min {\V {g}', \V {f}'}  \MC \IP {\V {1}, \V {f}'} \NR
   \NC \Rm {subject} \; \Rm {to} \MC \V {g}' \leq \V {f}' \NR
   \NC \MC - \V {g}' \leq \V {f}' \NR
   \NC \MC \M {P}^\Adj \M {P} \V {g}' \leq \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
   \NC \MC - \M {P}^\Adj \M {P} \V {g}' \leq - \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
\stopcases \NR
}
\I Output \m {\Hat {\M {H}} \LA \M {K} \Rm {vec}^{-1} \SB {\Hat {g}} \M {K}^\Adj}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Performance Metric}
{
\I Let the \m {\T {\chi}}, the relative 2-norm error, be the performance metric.

@@

\I Also define \m {\chi} by plugging in \m {\V {d}} into \m {\T {\chi}}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=2N_Y}}
{
\blank [big]
\externalfigure [assorted-narrow-medium-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=2N_Y}}
{
\blank [big]
\externalfigure [assorted-narrow-very-big-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=3N_Y}}
{
\blank [big]
\externalfigure [assorted-wide-medium-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=3N_Y}}
{
\blank [big]
\externalfigure [assorted-wide-very-big-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\It {ibid.}, low signal, assorted, \m {N_H=16=3N_Y}}
{
\blank [big]
\externalfigure [assorted-medium-low-signal-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time, assorted, \m {N_H=16}}
{
\blank [big]
\externalfigure [assorted-medium-time.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{
\I DS wins other method in the range drawn.

\I \m {\chi} does not show trend that \m {\T {\chi}} predicts.

\I The relaxed sparsity might compromise DS performance

@@

\I Soft thresholding (green) guesses wrong nonzero components (black), and the estimated value (orange) deteriorates
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity}
{
\I Let \m {C} denote big-O estimation of complexity, then we argue in the treatise
\Disp {
\NC C_{\Rm {OMP}} =\NC \mathcal {O} \SB {N_H^2 \log N_Y} \NR
\NC C_{\Rm {Lasso}} =\NC \mathcal {O} \SB {N_H^6} \NR
\NC C_{\Rm {DS}} =\NC \mathcal {O} \SB {N_{H}^6} \NR
}

\I Fitting runtime statistics one has
\Disp {
\NC \T {t}_{\Rm {OMP}} \NC \eqsim \mathcal {O} \SB {N_H^{3.6}} \NR
\NC \T {t}_{\Rm {Lasso}} \NC \eqsim \mathcal {O} \SB {N_H^{4.8}} \NR
\NC \T {t}_{\Rm {DS}} \NC \eqsim \mathcal {O} \SB {N_H^{8.3}} \NR
}
}

>>>>

% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Linear Programming}
{
\I DS is equivalent to a linear program, which allows more efficient convex programming methods to be used.
(Variables with tilde denote the real representation of complex matrices and vectors.)
\Disp {
\NC \Hat {\T {\V {g}}}, \Hat {\T {\V {f}}}
\LA \NC \startcases
   \NC \Min {\T {\V {g}}', \T {\V {f}}'}  \MC \IP {\V {1}, \T {\V {f}}'} \NR
   \NC \Rm {subject} \; \Rm {to} \MC \T {\V {g}}' \preceq \T {\V {f}}',
   \quad \MC - \T {\V {g}}' \preceq \T {\V {f}}' \NR
   \NC \MC \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
   \NC \MC - \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq - \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
\stopcases \NR
}
\I Output \m {\Hat {\M {H}} \LA \M {K} \Rm {vec}^{-1} \SB {\Hat {\T {\V {g}}}} \M {K}^\Adj}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Performance Metric}
{
\I Let the \m {\T {\chi}}, the relative 2-norm error, be the performance metric.

@@

\I Also define \m {\chi} by plugging in \m {\V {d}} into \m {\T {\chi}}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=2N_B}}
{
\blank [big]
\externalfigure [assorted-narrow-medium-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=2N_B}}
{
\blank [big]
\externalfigure [assorted-narrow-very-big-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=3N_B}}
{
\blank [big]
\externalfigure [assorted-wide-medium-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=3N_B}}
{
\blank [big]
\externalfigure [assorted-wide-very-big-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\It {ibid.}, low signal, \m {N_H=16=3N_B}}
{
\blank [big]
\externalfigure [assorted-medium-low-signal-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time, assorted, \m {N_H=16}}
{
\blank [big]
\externalfigure [assorted-medium-time.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{
\I DS wins other method in the range drawn.

\I \m {\chi} does not show the trend that \m {\T {\chi}} predicts.

\I The relaxed condition on sparsity may have compromised performance of DS

@@

\I Soft thresholding (green) guesses wrong nonzero components (black), and the estimated value (orange) deteriorates
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity}
{
\I Let \m {C} denote big-O estimation of complexity, then we argue in the treatise
\Disp {
\NC C_{\Rm {OMP}} =\NC \mathcal {O} \SB {N_H^2 \log N_B} \NR
\NC C_{\Rm {Lasso}} =\NC \mathcal {O} \SB {N_H^6} \NR
\NC C_{\Rm {DS}} =\NC \mathcal {O} \SB {N_{H}^6} \NR
}

\I Fitting runtime statistics one has
\Disp {
\NC \T {C}_{\Rm {OMP}} \NC \eqsim \mathcal {O} \SB {N_H^{3.6}} \NR
\NC \T {C}_{\Rm {Lasso}} \NC \eqsim \mathcal {O} \SB {N_H^{4.8}} \NR
\NC \T {C}_{\Rm {DS}} \NC \eqsim \mathcal {O} \SB {N_H^{8.3}} \NR
}
}

### 2020-11-10 presentation/4_conclusion.tex
Delete obsolete formulation on SOCP

\Frame {Conclusion}
{
\I We estimate MIMO mm-Wave channel \m {\M {H}} by using a modified DS.

\I We justify DS in present scenario with almost-sparse \m {\V {g}}, and show the RIP of effective beamformer \m {\M {P}}.

\I We propose a error norm analysis of DS in terms of parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigate the asymptotic successful probability.

\I DS may be converted to be a linear program to reduce complexity.

\I While DS does appear superior, it has complexity much greater than OMP.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References (1/2)}
{
{\tfx
\I A Alkhateeb, O E Ayach, G Leus, R W Heath, \Quote {Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems}, \It {IEEE Journal of Selected Topics in Signal Processing} 8(5), 2014

>>>>

\Frame {Conclusion}
{
\I We estimate MIMO mm-Wave channel \m {\M {H}} by using modified DS.

\I We justify DS under relaxed condition on sparsity of \m {\V {g}}, and demonstrate the RIP of effective beamformer \m {\M {P}}.

\I We analyze the error norm of DS in terms of \m {N_H}, \m {N_B}, and \m{L}, and approximate the asymptotic failure probability.

\I By simulation we see that DS appears to be superior to other methods.

\I DS trades off low time and space complexity for high precision.
For OMP, the opposite is true.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References (1/2)}
{
{\tfx
\I A Alkhateeb, O E Ayach, G Leus, R W Heath, \Quote {Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems}, \It {IEEE Journal of Selected Topics in Signal Processing} 8(5), 2014

### 2020-11-10 treatise/1_introduction.tex
Delete obsolete formulation on SOCP

Indeed, the estimation of MIMO channel amounts to determining all parameters of the channel, which is a big square matrix of dimension \m {N_H}, the number of antennae.
Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], reducing the number of paths, and that's when a recent development called compressive sensing may help.
Generally speaking, it is a technique for reconstructing a underdetermined linear system, when the sparsity of solution guarantees successful recovery in most cases.

@@

Candès and Tao \cite [Can05] first embarked a series of investigation on the problem.
Let us say the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
%
\DispNum {N:p:Nm:Nm} {
\NC N_p \gg \NC N_m \NR
}
%
To start, consider \m {\V {x}, \V {x}' \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}, and the linear transformation
%
\DispNum {y:y:Qx:Qx} {
\NC \V {y}
=\NC \M {Q} \V {x} + \V {z} \NR
}
Certainly, \m {\M {Q} \RB {\V {x}_1 - \V {x}_2} = 0}, then \m {\V {x}_1, \V {x}_2} are indistinguishable.
But if \m {\V {x}} is supposed to be sparse, it essentially restricts the system so much that we obtain unique solution for most of the time.

@@

Candès and Tao showed that, in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with fewer than \m {N_p} measurement, under overwhelming probability.

@@

From the computational perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, allows techniques from convex optimization to be used.
In fact, Candès \& Romberg provided an example implementation on their website (Candès \& Romberg \cite [CaR05]).
In addition, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a Linear Program (hereafter LP), rendering convex programming technique applicable.

Here the constant \m {\d_s} in Definition [1] is crucial:
we must make a series of carefully chosen but random measurement.
We can't just take \m {\M {Q}} to be any unitary matrix, for which it is trivial that \m {\d_s =0}.
One common proposal is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive a algorithm that efficiently finds RIP matrices.

Back at the ranch, recall that the channel estimation has been considered infeasible in the MIMO setting, but luckily, physical evidences suggest that mm-wave channels are in fact sparse in the frequency domain.
Some scholars have thus applied compressive sensing techniques.
An early attempt was Bajwa et.\ al.\ \cite [BHS10], where they argued that 
if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
The accompanying note by the same group \cite [BHR08] showed that \m {X} is RIP for overwhelming probability, justifying their work.
And \cite [BHR08], which considered a linear time-invariant channel, showed that if the convolution with channel response can be seen as a linear system, whose sensing matrix has RIP of overwhelmingly probability, and DS is readily applied.

@@

At the same time, Tropp and Gilbert \cite [TrG07b] suggested that a greedy algorithm called Orthogonal Matching Pursuit (OMP), which also makes use of an i.i.d.\ random matrix, may also reconstruct the sparse signal sufficiently well in an overwhelmingly probability. 
In so doing, we still consider \Rf {y:y:Qx:xz}, and pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}.

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m {\M {Q} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
%
\item Initialize
%
\Disp {
\NC \V {r}
\LA \NC \V {y} \NR
%
\NC S
\LA \NC \varnothing \NR
}
\item Start the loop with counter \m {i \LA 1}.
\item Find
%
\DispNum {c:c:i0:ir} {
\NC c
\LA \NC \underset {i =0, \dots, N_p-1} {\Rm {argmax}}
\Nm {\M {Q} _{\SB {:,i}} \V {r}} \NR
}
%
and insert \m {S \LA S \cup {i}}.
\item Compute
%
\DispNum {Q:Q:QS:Qy} {
\NC \M {Q} ^\ddagger
\LA \NC \RB {\M {Q} _{\SB {S}} ^\Adj \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\Adj \NR
%
\NC \V {r}
\LA \NC \V {y} -\M {Q} _{\SB {S}} ^\Adj \M {Q} ^\ddagger \V {y} \NR
}
\item Break if
%
\DispNum {r:2:h':h'} {
\NC \VNm {\V {r}} _2
<\NC \eta \NR
}
%
where \m {\VNm {\M {Q} ^\ddagger} _1} denotes the operator norm.
\item Output 
%
\DispNum {g:g:Qy:Qy} {
\NC \Hat {\V {g}}
\LA \NC \M {Q} ^\ddagger \V {y} \NR
}
\stopitemize
}
%
Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the number of estimated nonzero components of \m {\V {x}} (here we have slightly abused the usage of subscript).
From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a performance guarantee.
It is instructive to note that the matrix consisting of a collection of columns that likely spans \m {\V {x}} plays the role of the sensing matrix in the previous section.

@@

In this treatise, we illustrate, by the case of uniformly random angles, that DS may outperform OMP among other methods, and the nature of convex program also guarantees its performance.
In chapter 2 we shall see that the effective beamformer may serve as the sensing matrix having RIP for high probability.
The sparsity can be exploited this way, and DS may readily be applied.
In chapter 3, along the lines of Candès and Tao \cite [CaT07], we give a bound (which holds for high probability) on expected error norm, expressed in terms of the suggested sparsity and the number of paths.
In chapter 4, we remark that DS can be cast as a linear program, for which efficient algorithms are known.
Numerical results show that in our configuration DS is superior to OMP among other methods, but is achieved at the cost of higher complexity.

>>>>

Indeed, the estimation of MIMO channel amounts to determining all parameters of the channel representation.
Our task amounts to invert a linear system whose dimension is the number of antennae.
Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], reducing the number of paths, and that's when a recent development called compressive sensing may help.
Generally speaking, it is a technique for reconstructing a underdetermined linear system, when the sparsity of solution guarantees successful recovery in most cases.

@@

Candès and Tao \cite [Can05] first embarked a series of investigation on the problem.
Let us say the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
%
\DispNum {N:p:Nm:Nm} {
\NC N_p \gg \NC N_m \NR
}
%
To start, consider \m {\V {x}, \V {x}' \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}, and the linear transformation
%
\DispNum {y:y:Qx:Qx} {
\NC \V {y}
=\NC \M {Q} \V {x} \NR
}
Certainly, \m {\M {Q} \RB {\V {x}_1 - \V {x}_2} = 0}, then \m {\V {x}_1, \V {x}_2} are indistinguishable.
But if \m {\V {x}} is supposed to be sparse, it essentially restricts the system so much that we obtain unique solution for most of the time.

@@

Candès and Tao showed that, in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with fewer than \m {N_p} measurements, under overwhelming probability.

@@

The formulation as an \m {\ell_1} minimization problem, which is convex.
From the computational perspective, this allows techniques from convex optimization to be used.
In fact, Candès and Romberg provided an example implementation on their website \cite [CaR05].
In addition, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear Program, rendering convex programming technique applicable.

Here the constant \m {\d_s} in Definition [1] is crucial:
we must make a series of carefully chosen but random measurements.
We can't just take \m {\M {Q}} to be any unitary matrix, for which it is trivial that \m {\d_s =0}.
One common proposal is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive a algorithm that efficiently finds RIP matrices.

Back at the ranch, recall that the channel estimation has been considered infeasible in the MIMO setting, but luckily, physical evidences suggest that mm-wave channels are in fact sparse in the frequency domain.
Some scholars have thus applied compressive sensing techniques.
An early attempt was Bajwa et.\ al.\ \cite [BHS10], where they argued that 
if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
The accompanying note by the same group \cite [BHR08] showed that \m {X} has RIP for overwhelming probability, justifying their work.
And \cite [BHR08], which considered a linear time-invariant channel, showed that if the convolution with channel response can be seen as a linear system, whose sensing matrix has RIP of overwhelmingly probability, and DS is readily applied.

@@

At the same time, Tropp and Gilbert \cite [TrG07b] suggested likewise that a greedy algorithm called orthogonal matching pursuit (OMP) may reconstruct a sparse signal sufficiently well in an overwhelmingly probability. 
In the situation of \Rf {y:y:Qx:xz}, we would pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}.

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m {\M {Q} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
%
\item Initialize
%
\Disp {
\NC \V {r}
\LA \NC \V {y} \NR
%
\NC S
\LA \NC \varnothing \NR
}
\item Start the loop with counter \m {i \LA 1}.
\item Find
%
\DispNum {c:c:i0:ir} {
\NC c
\LA \NC \underset {i =0, \dots, N_p-1} {\Rm {argmax}}
\Nm {\M {Q} _{\SB {:,i}} \V {r}} \NR
}
%
and insert \m {S \LA S \cup {i}}.
\item Compute
%
\DispNum {Q:Q:QS:Qy} {
\NC \M {Q} ^\ddagger
\LA \NC \RB {\M {Q} _{\SB {S}} ^\Adj \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\Adj \NR
%
\NC \V {r}
\LA \NC \V {y} -\M {Q} _{\SB {S}} ^\Adj \M {Q} ^\ddagger \V {y} \NR
}
\item Break if
%
\DispNum {r:2:h':h'} {
\NC \VNm {\V {r}} _2
<\NC \eta \NR
}
%
where \m {\VNm {\M {Q} ^\ddagger} _1} denotes the operator norm.
\item Output 
%
\DispNum {g:g:Qy:Qy} {
\NC \Hat {\V {g}}
\LA \NC \M {Q} ^\ddagger \V {y} \NR
}
\stopitemize
}
%
Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the number of estimated nonzero components of \m {\V {x}} (here we have slightly abused the usage of subscript).
From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a performance guarantee.

OMP also makes use of an entrywise i.i.d.\ random matrix.
It is instructive to note that the matrix columns is likely to span \m {\V {x}}, playing a role similar to the sensing matrix in the case of DS.

@@

In this treatise, we illustrate that DS may outperform OMP and other methods.
In chapter 2 we shall see that the effective beamformer may serve as the sensing matrix having RIP for high probability.
The sparsity can be exploited this way, and DS may readily be applied.
In chapter 3, along the lines of Candès and Tao \cite [CaT07], we give a bound (which holds for high probability) on expected error norm, expressed in terms of the suggested sparsity and the number of paths.
In chapter 4, we remark that DS can be cast as a linear program, for which efficient algorithms are known.
Numerical results show that in our configuration, where we have uniformly random angles of departure and arrival, DS is superior, but is achieved at the cost of higher complexity.
